### 2015-07-02 narrative/naming-service.tex
saved some work. TBC.

Given the well documented difficulties with POSIX-compliant naming and our
potentially heavily decomposed objects, we must take a new approach to naming.
Adding complexity is data migration based on system pressures. Our naming
service must support sufficient information to discover or track all variables
pieces across the entire storage hierarchy.

Hierarchical Storage Management (HSM) systems offer a strct caching approach
for managing different storage capacities trading off performance for capacity.
By maintaining a single namespace across all tiers, it is possible to list a
single directory view with files stored at different tiers. While this approach
to managing multi-tier storage works for whole files that fit on single logial
devices, it is far from ideal for scientific simulations.

Our goal with this proposal is to offer a similar capability, but use a finer
granularity and also manage discovering where the data may have migrated to
based on system pressures. Instead of a single file such as might be used to
store an entire timestep output for a simulation, we will demonstrate offering
the same capability at a subset of a single variable level. By shifting to a
finer-grained approach, we will enable more effective use of close/fast/small
storage tiers and manage the impact when there is insufficient space forcing
data to move. Traiditional HSM stores an entire file on a tier making room if
insufficient space is available. With this shift to a partial variable
granularity, a 1 PB output with 500 GB of ``high interest'' data can limit this
costly tier ussage to just 500 GB greatly enhancing usability. This reduces
pressure forcing data migration, but does not prevent it. We still need to be
able to find the data should it move based on system pressure.

>>>>

Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes data into potentially large number of objects, 
we must take a new approach to naming.
Data migration, as a result of system pressures or user/system policies,
further adds to the complexity of managing naming and discovery. Our naming
service must maintain sufficient metadata information, track objects
as they move across storage layers, and facilitates data discovery.

Hierarchical Storage Management (HSM) systems \cite{hsm} offer a strict caching approach
for managing different storage capacities trading off performance for capacity.
By maintaining a single namespace across all tiers, it is possible to list a
single directory view with files stored at different tiers. While this approach
to managing multi-tier storage works for whole files that fit on single logial
devices, it is far from ideal for scientific simulations.

Our goal with this proposal is to offer a similar capability but with a finer
granularity leveraging the inner structure of scientific data, 
and manage discovering efficiently, where the data may
be split and placed on several storage layers, or may have migrated
based on system pressures. Instead of a single file such as might be used to
store an entire timestep output for a simulation, we will demonstrate offering
the same capability at a subset of a single variable level. By shifting to a
finer-grained approach, we will enable more effective use of close/fast/small
storage tiers and manage the impact when there is insufficient space forcing
data to move. Traiditional HSM stores an entire file on a tier making room if
insufficient space is available. With this shift to a partial variable
granularity, a 1 PB output with 500 GB of ``high interest'' data can limit this
costly tier ussage to just 500 GB greatly enhancing usability. This reduces
pressure forcing data migration, but does not prevent it. We still need to be
able to find the data should it move based on system pressure.
